### 2016-06-24 responseToReviewers.tex

\begin{figure}[htbp]
\centering
\includegraphics{Figures/wmhPipeline.png}
\caption{\textcolor{blue}{Workflow illustration for the proposed pipeline.  Processing of the multi-modal
input MRI for a single subject, using the multi-modal symmetric template, results in
the generation of the feature images.  These feature images are used as input to the
Stage 1 RF model producing the initial RF probability map estimates.  The Stage 1
voting maps, the original feature images, and the Stage 2 RF model result in the
final voting maps which includes the WMH probability estimate.  Note that the RF models
are constructed once from a set of training data which are processed using the
same feature-construction pipeline as the single-subject input MRI.}}
\end{figure}

\clearpage

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\hypertarget{ref-Marquez-de-la-Plata:2007aa}{}
1. Marquez de la Plata C, Ardelean A, Koovakkattu D, Srinivasan P,
Miller A, Phuong V, Harper C, Moore C, Whittemore A, Madden C, et al.
Magnetic resonance imaging of diffuse axonal injury: Quantitative
assessment of white matter lesion volume. J Neurotrauma.
2007;24(4):591--8.

\hypertarget{ref-Avants:2014aa}{}
2. Avants BB, Tustison NJ, Stauffer M, Song G, Wu B, Gee JC. The Insight
ToolKit image registration framework. Front Neuroinform. 2014;8:44.

\hypertarget{ref-Yushkevich:2006aa}{}
3. Yushkevich PA, Piven J, Hazlett HC, Smith RG, Ho S, Gee JC, Gerig G.
User-guided 3D active contour segmentation of anatomical structures:
Significantly improved efficiency and reliability. Neuroimage.
2006;31(3):1116--28.

\hypertarget{ref-Tustison:2014ab}{}
4. Tustison NJ, Cook PA, Klein A, Song G, Das SR, Duda JT, Kandel BM,
Strien N van, Stone JR, Gee JC, et al. Large-scale evaluation of aNTs
and freeSurfer cortical thickness measurements. Neuroimage.
2014;99:166--79.

\hypertarget{ref-Avants:2011aa}{}
5. Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open source
multivariate framework for \(n\)-tissue segmentation with evaluation on
public data. Neuroinformatics. 2011;9(4):381--400.

\hypertarget{ref-Tustison:2015aa}{}
6. Tustison NJ, Shrinidhi KL, Wintermark M, Durst CR, Kandel BM, Gee JC,
Grossman MC, Avants BB. Optimal symmetric multimodal templates and
concatenated random forests for supervised brain tumor segmentation
(simplified) with aNTsR. Neuroinformatics. 2015;13(2):209--25.

\hypertarget{ref-landman2011}{}
7. Landman BA, Huang AJ, Gifford A, Vikram DS, Lim IAL, Farrell JAD,
Bogovic JA, Hua J, Chen M, Jarso S, et al. Multi-parametric neuroimaging
reproducibility: A 3-T resource study. Neuroimage. 2011;54(4):2854--66.

\hypertarget{ref-Moen:2014aa}{}
8. Moen KG, Brezova V, Skandsen T, Håberg AK, Folvik M, Vik A. Traumatic
axonal injury: The prognostic value of lesion load in corpus callosum,
brain stem, and thalamus in different magnetic resonance imaging
sequences. J Neurotrauma. 2014;31(17):1486--96.

\hypertarget{ref-Anbeek:2004aa}{}
9. Anbeek P, Vincken KL, Osch MJP van, Bisschops RHC, Grond J van der.
Probabilistic segmentation of white matter lesions in mR imaging.
Neuroimage. 2004;21(3):1037--44.

\hypertarget{ref-Tustison:2013ac}{}
10. Tustison NJ, Avants BB. Explicit B-spline regularization in
diffeomorphic image registration. Front Neuroinform. 2013;7:39.

\hypertarget{ref-Avants:2011ab}{}
11. Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. A
reproducible evaluation of ANTs similarity metric performance in brain
image registration. Neuroimage. 2011;54(3):2033--44.
